Visual Diagnostics for Constrained Optimisation with Application to Guided Tours

### 2021-03-02 paper/zhang-cook-laa-langrene-menendez.Rmd
change color for polish example

The holes index function used for all the examples before this section produces a smooth interpolation, while this is not the case for all the indices. A 1D projection function, $I^{nk}(n)$, compares the projected data, $\mathbf{Y}_{n \times 1}$, to a randomly generated normal distribution, $\mathcal{N}_{n \times 1}$, based on the Kolmogorov test. Let $F_{.}(n)$ be the ECDF function, with two possible subscripts $Y$ and $\mathcal{N}$ representing the projected and randomly generated data, and $n$ denoting the number of observation, the Normal Kolmogorov index, $I^{nk}(n)$, is defined as:

$$I^{nk}(n) = \max \left[F_{Y}(n) - F_{\mathcal{N}}(n)\right]$$
With a non-smooth index function, two research questions are raised:

>>>>

The holes index function used for all the examples before this section produces a smooth interpolation, while this is not the case for all the indices. A 1D projection function, $I^{K}(n)$, compar‚es the projected data, $\mathbf{Y}_{n \times 1}$, to a randomly generated normal distribution, $\mathcal{N}_{n \times 1}$, based on the Kolmogorov test. Let $F_{.}(n)$ be the ECDF function, with two possible subscripts $Y$ and $\mathcal{N}$ representing the projected and randomly generated data, and $n$ denoting the number of observation, the Normal Kolmogorov index, $I^{nk}(n)$, is defined as:

$$I^{K}(n) = \max \left[F_{Y}(n) - F_{\mathcal{N}}(n)\right]$$
With a non-smooth index function, two research questions are raised:

### 2021-03-02 paper/zhang-cook-laa-langrene-menendez.tex
change color for polish example

The holes index function used for all the examples before this section
produces a smooth interpolation, while this is not the case for all the
indices. A 1D projection function, \(I^{nk}(n)\), compares the projected
data, \(\mathbf{Y}_{n \times 1}\), to a randomly generated normal
distribution, \(\mathcal{N}_{n \times 1}\), based on the Kolmogorov
test. Let \(F_{.}(n)\) be the ECDF function, with two possible
subscripts \(Y\) and \(\mathcal{N}\) representing the projected and
randomly generated data, and \(n\) denoting the number of observation,
the Normal Kolmogorov index, \(I^{nk}(n)\), is defined as:

\[I^{nk}(n) = \max \left[F_{Y}(n) - F_{\mathcal{N}}(n)\right]\] With a
non-smooth index function, two research questions are raised:

>>>>

The holes index function used for all the examples before this section
produces a smooth interpolation, while this is not the case for all the
indices. A 1D projection function, \(I^{K}(n)\), compar‚es the projected
data, \(\mathbf{Y}_{n \times 1}\), to a randomly generated normal
distribution, \(\mathcal{N}_{n \times 1}\), based on the Kolmogorov
test. Let \(F_{.}(n)\) be the ECDF function, with two possible
subscripts \(Y\) and \(\mathcal{N}\) representing the projected and
randomly generated data, and \(n\) denoting the number of observation,
the Normal Kolmogorov index, \(I^{nk}(n)\), is defined as:

\[I^{K}(n) = \max \left[F_{Y}(n) - F_{\mathcal{N}}(n)\right]\] With a
non-smooth index function, two research questions are raised:
